Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-08-31 1_introduction/introduction.tex
no message

The rest of the paper is organized as follows:
\begin{itemize}
	\item In Chapter~\ref{sec:relatedwork}, related studies in process mining area are presented. 
	\item In Chapter~\ref{sec:background}, background information for the relevant topics is explained.
	\item In Chapter~\ref{sec:methodology}, methodology proposed in this study is presented with detail.
	\item In Chapter~\ref{sec:results-and-discussions}, methodology of this study is applied on datasets and results are discussed.
	\item In Chapter~\ref{sec:conclusion-and-future-work}, summary of this study is presented with the final remarks and pointers for future work. 
\end{itemize}

>>>>

The rest of the paper is organized as follows:
\begin{inparaenum}
	\item In Section~\ref{sec:relatedwork}, related studies in process mining area are presented. 
	\item In Section~\ref{sec:background}, background information for the relevant topics is explained.
	\item In Section~\ref{sec:methodology}, methodology proposed in this study is presented with detail.
	\item In Section~\ref{sec:results-and-discussions}, methodology of this study is applied on datasets and results are discussed.
	\item In Section~\ref{sec:conclusion-and-future-work}, summary of this study is presented with the final remarks and pointers for future work. 
\end{inparaenum}
